The Evolution of National AS Chokepoints and Their Connection to Internet Freedom

### 2018-06-28 Paper/paper.tex
Added Updated Draft

\graphicspath{{./images/}}

\begin{document}
\begin{multicols}{2}

\section{Abstract}     
Paths on the Autonomous Systems (AS) graph of the Internet
derived from the Border Gateway Protocol (BGP) can be used by researchers to
understand the dynamics of Internet topology and to interpret how that
topology may enable nations to enact censorship, surveillance, or other
Internet control measures. Unfortunately datasets of these paths are not
generally made publicly available, and paths collected from measurements such as
traceroute measurements or BGP probes tend to be incomplete. Simulation
frameworks have been used to generate AS paths based on empirical AS graphs.
We have reimplemented one such framework, BGPSim \cite{quicksand} in Python as
an efficient, open source BGP path simulation tool called BGPSimPy. With this
tool we produced publicly available routing tree datasets that will enable
future research on AS level topology. Previous research endeavors in this
direction have only identified chokepoints in single snapshots. We apply the
path simulation and routing tree datasets to view snapshots of the Internet
over multiple years in order to introduce a new technique to investigate the
evolution of the complex and dynamic AS level Internet topology. As an
application of the routing trees we compare multiple qualitative sources of
Internet freedom and censorship with chokepoint metrics in order to interpret
the relationship between AS level topology and actual censorship activity.

@@

The primary struggle facing Internet topology researchers is
a lack of ground truth data. Paths on the AS level of the Internet are
incomplete and sometimes inaccurate {\color{blue}cite?}. Additionally, AS business
relationships are confidential and not publicly available. In this absence of
solid empirical data, a technique for inferring AS relationships and a
technique for inferring BGP paths are needed to study AS-level topology and
evolution. The first effective relationship inference algorithm was developed
by Gao in \cite{gao}. This algorithm was limited in that it focused on
maximizing the occurrences of the valley-free rule on the AS graph, which has
been shown to not always hold {\color{blue}cite?}. Additionally, Gao's algorithm was
verified against a single tier-1 provider's ground truth data. A more
verifiable correct set of AS relationships was developed by the Center for
Applied Internet Data Analysis (CAIDA) \cite{CAIDApaper}. These relationships,
which were generated using Gao's algorithm and other inference techniques,
were verified against a larger ground truth dataset, and didn't require that
the valley-free rule always hold. This leads to more realistic relationships. AS
relationships do not tell the whole story of AS-level topology, however. In
order to identify chokepoints in the AS graph, it is necessary to determine
the paths that Internet traffic follows. Researchers either use a measurement
tool like traceroute or BGP AS-path announcement data to determine AS paths.
These techniques have been shown to yield an incomplete and innacurate set of
paths {\color{blue}cite?}. It is also important that paths from all ASes be utilized to
get a complete picture of Internet topology. One technique for generating such
a set of paths was developed by Gill et al. in \cite{quicksand}. The algorithm
developed in \cite{quicksand}, called BGPSim, uses a modified breadth-first
search on an AS graph with defined relationships, as in from the CAIDA
dataset. The breadth first search traverses the AS graph starting from a root
node, and the search traverses edges according to priorities related to the
relationships defined by Gao. The priorities, in the order they are integrated
into the algorithm, are: Shortest Path (SP), Local Preference (LP), and Tie-
break (TB). The resultant paths are ideal according to economic concerns of AS
admins.     

@@

\section{BGPSimPy}
In order to conduct an analysis on AS level topology, the paths
generated by the Border Gateway Protocol (BGP) have to be modeled. A
traditional approach is to use a tool like traceroute to collect paths via
measurement, or at a larger scale use a selection of BGP data collectors with
a tool like BGPStream \cite{bgpstream} \cite{traceroute}. Unfortunately, these
techniques require extensive collection time and are still susceptible to
errors and incomplete data. There is no readily available BGP path dataset
with which to study. Thus, researchers must turn to simulation to find
accurate BGP paths.     
\par One such simulation framework, the previously
mentioned BGPSim, was developed by Gill et al. \cite{quicksand} as a tool for
quickly estimating AS paths from an input AS graph. This AS graph could be
taken from a set of inferred AS relationships, such as the CAIDA AS
relationship dataset \cite{CAIDA}. BGPSim outputs routing trees, which contain
all paths from leaf ASes to the root AS, for each AS in the AS graph. The
routes are selected using a modified breadth-first search that selects with
the following priorities: shortest path, local preference (using the rules
from Gao \cite{Gao}), and finally tie break of all equally good paths. With
these priorities, BGPSim generates a realistic collection of AS level paths,
which are ideal for use in Internet topology studies.
\par 
Unfortunately, BGPSim is not ready to deploy immediately and easily, as would be necessary
for a tool dedicated to allow fast monitoring of the Internet's overall state.
This is largely due to the fact that BGPSim is written in C\# (affecting its
ability to be used in a cross-platform way) with DryadLinq (a deprecated C\#
library) for distributed computing. As a remedy to these problems, we have
reimplemented BGPSim under the name BGPSimPy. BGPSimPy is written purely in
python, making it cross platform and easy to integrate. Additionally,
distributed computing is now achieved with MPI using mpi4py, a framework that
is supported on many computer clusters.

\section{Generating Routing Trees}
AS level Internet topology research is plagued
by a lack of publicly available path data. Path inference is also
computationally expensive for the entire Internet, prohibiting continuous
research and Internet monitoring. Thus, we have chosen to release the routing
tree datasets generated for this paper. This is a major contribution to
Internet research, and will allow new endeavors to investigate Internet
topology relationships on an unprecedented scale. As a focus of this paper,
and an example application, we use these routing trees to examine topological
evolution of the Internet and its relationships to Internet freedom and
censorship.

\section{Applications of Routing Trees}
\subsection{Measuring Chokepoints in AS-level Paths}
Once we generated routing trees, we
could use the paths to identify chokepoints, or ASes that intercept large
portions of paths, on the AS graph. Specifically, we chose to evaluate border
ASes, or ASes that could reach an AS registered to a different nation with one
hop. By selecting border ASes we could locate the ASes that intercepted
traffic into a nation (via out-to-in paths), as in a foreign attempt to access
a domestic website, or ASes that intercepted traffic out of a nation, as in a
domestic attempt to access a foreign website (via in-to-out paths). We choose
to make a distinction between these two path types to better understand the
implications of the chokepoints belonging to each nation.
\par To evaluate border ASes we use the metric of chokepont potential, defined here to be the
ratio of the number of paths intercepted by a border AS to the number of paths
for that nation, as shown in equation \ref{eqn:chokePointPotential}. This
metric is calculated separately for both in-to-out paths and out-to-in paths.
This calculation is performed by traversing the routing trees and keeping
record of which border nodes intercept each path, as well as what path type is
currently being traversed with regards to the host nation of the border AS in
question. Once all paths are traversed, the totals are compiled together, with
a chokepoint potential value stored for each border AS.
\par 
The chokepoint potentials of the border ASes allowed us to investigate the state of the AS-
level topology of the Internet for any given set of initial AS relationships.
We first looked at how many ASes each nation is required to control to
intercept a percentage of paths. For this test, we chose 90\%, as this would
indicate a clear control of Internet paths for the given country and was also
the percentage used in \cite{throats}. Additionally, we determined this value
for each nation for multiple timestamps, yielding our initial picture of the
evolution of Internet topology. The results of this test for some nations of
interest are shown in figure \ref{fig:NumToIntercept}.

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{NodesNeeded}
	\captionof{figure}{Number of border nodes needed to control 90\% of paths for various nations}\label{fig:NumToIntercept}
\end{Figure}

\par
These results give an idea of how the Internet has evolved for different nations. Some nations,
particularly China, have evolved to a state where it is significantly easier
to intercept paths. Others, for instance Brazil, have become more open with
regards to the chokepoint nature of border ASes. These results are even more
striking when one considers that the number of ASes globally has drastically
increased over the years, amplifying the effect of higher chokepoint
potentials. The number of ASes in the CAIDA AS relationship dataset in 2012
was 43,274 in January, while in January of 2018 the count was 60,006.
Next, we took a more fine-grained approach to investigate the dynamics and
evolution of AS-level chokepoints. For each nation, we sorted the border ASes
in descending order into a list, so that the first AS in the list was the AS
with the highest chokepoint potential. Then, we selected each AS from the list
and kept track of the ratio of paths intercepted. This test allowed us to
investigate the ease with which different nations could control paths at
multiple timestamps. Additionally, this experiment illuminates that the
topological state of a nation in regards to border ASes is often complex and
dynamic. Since nations possess wide variations in AS count, this data is best
visualized on a semi-logarithmic scale. The different timestamps are shown in
different colors, where red is the furthest in the past and blue is the most
recent. These results are depicted in \ref{fig:chokepoint}.

\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{single_AU}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{single_BR}
	\end{subfigure}
	\\
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{single_CN}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{single_DE}
	\end{subfigure}
	\\
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{single_GB}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{single_IR}
	\end{subfigure}
	\\
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{single_US}
	\end{subfigure}

	\caption{Ratio of Paths Intercepted for a certain number of Border Nodes for multiple nations}\label{fig:chokepoint}
\end{figure*}

\par 
The variation between the different nations highlights the importance of measuring
chokepoints on the national level. Trends exist within a nation, but nations
tend to have surprisingly unique AS graph dynamics. China shows a striking
increase in chokepoint potential. In order to control 90% of paths, China has
to utilize a strikingly few number of ASes. This suggests an ever
strengthening backbone in the Chinese Internet. Conversely, the trend that
Brazil's capability to intercept paths is decreasing is also evident in these
results. This could be the effect of an expansion of infrastructure, leading
to more border ASes and more diverse paths in and out of the country. {\color{blue}Maybe
there is a source to support this?} Another interesting element of these
results is the dynamic behavior for some nations. It seems that in some cases,
when it becomes easier to control many paths, it becomes more difficult to
control all paths. {\color{blue}Not sure of implications, needs work here}

\subsection{Comparing Internet Topology with Freedom On The Net}
While research in the past \cite{throats} has connected AS-level chokepoints with the capability of
a nation to conduct censorship, linking the topology based measurements to
other attempts at measuring Internet freedom has not been done before to the
best of our knowledge. Such a connection would bridge the gap between a
dynamic system driven by many factors, both automatic and instituted, and
qualitative classification of nations.
\par Freedom House's Freedom On The Net
(FOTN) report \cite{FOTN}, is an annual ranking and analysis of Internet
freedom, interpreted from multiple measures including obstacles to access,
limits on content, and violations of user rights. The FOTN includes a ranking
of nations by a freedom index, where a higher number indicates a less free
Internet for that nation. The index is calculated from a series of questions
that are evaluated according to various sources regarding each nation. These
questions encompass multiple categories, including government filtering and
censorship of web traffic. In order to investigate whether the topology of a
nations ASes is related to Internet freedom, we compare the FOTN freedom index
with the ease with which a nation can control AS level paths. In figure
\ref{fig:fotn} we plot the number of ASes required for a nation to control 90%
of paths with that nation's freedom index for multiple timestamps of AS
relationships.

\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{fotn2012}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{fotn2015}
	\end{subfigure}
	\\
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{fotn2016}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{fotn2017}
	\end{subfigure}

	\caption{Ratio of Paths Intercepted for a certain number of Border Nodes for multiple nations}\label{fig:fotn}
\end{figure*}

\par For each date we fit the data with an ordinary least
squares linear regression, and found the relationship to be statistically
significant (all p-values are less than 0.05). {\color{blue}need some better way to show
exact p-values} The relationship shows that more free nations, as determined
by FOTN scores, tend to have a more difficult to control AS-level topology, as
in border nodes that control fewer portions of paths in and out of that
country. This suggests that either the desire of national governments to
control Internet traffic has impacted the layout of AS relationships, the
topology of the modern Internet has evolved in a way to enable more successful
filtering and blocking, or a combination of both. Up to this point it has been
assumed that Internet topology and Internet censorship are related, but this
has not been supported by both a measure of Internet freedom and actual AS-
level paths.

\subsection{Comparing Internet Topology with Empirical Censorship Data}

Another
technique for relating our chokepoint metric with censorship is to look at
empirical censorship data. One such dataset is provided by the Open
Observatory of Network Interference (OONI) \cite{OONI}. OONI is a project
wherein Internet users around the world use a tool (the ooniprobe) to examine
evidence of Internet censorship. The ooniprobe allows users to run a series of
tests, such as an HTTP requests that might be known to be blocked by certain
nations. The ooniprobe then compares the results of tests with previously
determined unblocked examples of the same tests. Results where the test
differs from expected are considered anomalies, and further heuristics can
determine if the anomalies are likely to be censorship events.
\par We examined
18 days of OONI data from January in 2018. We recorded the ratio of anomalies
in measurements for several classes of anomalous behavior to total
measurements carried out in each nation. We used the web connectivity test
from OONI that records the following fields to measure connectivity: DNS,
HTTP\_FAIL, HTTP\_DIFF, and TCP. Each of these fields are recorded as true or
false, according to whether the test resulted in a potential censorship event.
We then plotted the ratio of potential censorship events in the dataset
against a national metric of chokepoint potential. In this case, we again
looked at the number of border nodes required to intercept 90\% of AS-level
paths. The results of this test are plotted in figure \ref{fig:ooni}. A
relationship like the one seen in the FOTN data is not as clear, perhaps due
to the uneven sampling across nations. It is clear, however, that nations can
be classified both by its chokepoint potential and the occurrence of possible
censorship events. A nation, for instance, with a high ratio of web
connectivity anomalies with a high chokepoint potential can be considered a
censorship active nation with a strongly hierarchical AS topology. Thus, this
analysis serves as a monitoring tool for the state of nations on the Internet
in regards to actual censorship implementation, and potential for further
censorship.

\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{all_09}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{dns_09}
	\end{subfigure}
	\\
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{http_diff_09}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{http_fail_09}
	\end{subfigure}
	\\
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\linewidth]{tcp_09}
	\end{subfigure}

	\caption{Ratio of anomalies in OONI measurements compared to chokepoint potential}\label{fig:ooni}
\end{figure*}

@@

We have introduced an efficient technique for studying the AS-level topology of the Internet. Additionally,
we introduced the metric of chokepoint potential in order to evaluate the control that border nodes possess
over paths into and out of a nation. We have applied the routing trees generated by BGPSimPy along with the
chokepoint potential metric to present an overview of the evolution of the amount and strength of chokepoints
on the AS graph over the past 6 years. We also connected our analysis of AS-level chokepoints in a novel way to
both qualitative measures of Internet freedom and empirical censorship data. The former comparison reveals
a strong relationship between the chokepoint potential of a nation and its lack of Internet freedom, while the
former provides insight into the categories of nations, in regards to their implementations of censorship and
the layout of their AS relationships.

>>>>

\newcommand{\toolname}{{\color{blue}TOOL\_NAME }}

%Titles:
\title{The Evolution of National AS Chokepoints and Their Connection to
Internet Freedom}

\graphicspath{{./images/}}
\setlength{\parskip}{0pt}

\begin{document}
\raggedbottom
\maketitle
\begin{multicols}{2}

\section{Abstract}     
Paths on the Autonomous Systems (AS) graph of the Internet
derived from the Border Gateway Protocol (BGP) can be used by researchers to
understand the dynamics of Internet topology and to interpret how that
topology may enable nations to enact censorship, surveillance, or other
Internet control measures. Unfortunately datasets of these paths are not
generally made publicly available, and paths collected from measurements such as
traceroute or BGP probes tend to be incomplete. Simulation
frameworks have been used to generate AS paths based on inferred AS relationships.
We introduce \toolname, a suite of open source, cross platform, and efficient
tools for monitoring national chokepoints on the AS graph. We introduce chokepoint potential as an important measure of a nation's ability to 
control Internet traffic, either through censorship or surveillance.
Previous research endeavors in this
direction have only identified chokepoints in single snapshots. We apply our
path simulation and routing tree datasets to view snapshots of the Internet
over multiple years in order to introduce a new technique to investigate the
evolution of the complex and dynamic AS level Internet topology. Through this approach we
can more carefully evaluate the state of the Internet than was previously possible. As an
application of \toolname we compare Freedom House's Freedom On The Net (FOTN) score for
Internet freedom and with our chokepoint potential measure in order to interpret
the relationship between AS-level topology and actual censorship activity, providing an
illustration of new ways to monitor which governments can easily control the flow of 
information in their nations and whether they are acting on that potential.

\section{Introduction}

%The Internet is Dynamic and growing
The Autonomous Systems layer of the Internet has grown and changed dramatically over its history.
In the early 2000s, there were around 10,000 ASes connected to the global AS graph. Today there are
over 60,000 of these ASes. The locations and relationships of these ASes determine how many chokepoints
of AS-level routing exist and what strength these chokepoints have in regards to paths intercepted.
This rapid expansion of the AS graph suggests a dynamic system with behavior that is important for
understanding things like path robustness, AS hierarchies, and the potential for governments to control
information as it flows in and out of their borders. It is certain that structrural qualities of national
AS graphs have evolved differently from nation to nation, whether that be due to economic decision making, infrastructural
necessities, or efforts to build a powerful censorship and surveillance network.

%Current Events
\par
The Internet has been used as a tool for the citizens of authoritarian nations to voice opinions,
organize revolutionary movements, and connect with other nations' governments and citizens
to seek aid. Much of the organization, revolutionary momentum, and broadcasting
of happenings during the Arab Spring can be attributed to social media communications
through the Internet \cite{arabspring}. Because of this potential, national governments may
take interest in maximizing their ability to control the flow of information on the Internet.
%Censorship and Surveillance are growing phenomena
\par
Internet censorship and surveillance have become profound social and technical issues facing the world. The portion of the
global population that uses the Internet has increased substantially in recent years. According to the International Telecommunication Union,
the number of individual users of the Internet has increased from 1.024 million in 2005 to 3.578 million in 2017 \cite{itu}. Of the Internet
population, a majority of them are subject to some lack of Internet freedom. The 2017 Freedom on the Net report from freedom house reports that
64\% of Internet users belong to a nation with Internet that is not free or partly free \cite{FOTN}. It is evident that Internet control is
a powerful force for governments to wield. Whether or not AS-level topology supports these efforts is a research question pivotal to
an understanding of the dynamics of Internet censorship and surveillance.

%Diverse Censorship Architecture
\par
Every nation has a different layout and count of ASes. The censorship and surveillance strategies of nations also differ. For instance,
China both conducts keyword filtering in border ASes and in internal provincial nodes \cite{chinafiltering}. Another nation that conducts
extensive Internet censorship, Iran, has been found to route all of its Internet traffic through a centralized facility \cite{irancensor}.
Having views into the AS topology of a nation, then, will both help researchers identify nations that could easily conduct censorship and
also provide possible insight into what kind of censorship is likely being conducted. The measure of chokepoint potential, defined later in this paper,
is an effective way to capture the important properties of border ASes related to these capabilities.

% Major Contributions
\par
The primary contributions of our work are as follows: \textbf{1.} We introduce the measure of chokepoint potential and 
motivate its value as way to interpret the capability for a nation to enact censorship of its Internet traffic. \textbf{2.} We
provide an overview of the evolution of national AS-level chokepoints over time, showing the evolution of the Internet
allowing for a comparision between nations. \textbf{3.} We develop a new tool, \toolname, that provides the capability for
efficiently evaluating chokepoints for a given state of the Internet. Finally, \textbf{4.}, we show that our chokepoint measure
has a significant relationship to Internet freedom as measured by a qualitative source.

% Rest of Paper Layout
\par

\section{Background}

The AS-layer of the Internet is the highest level of organization of the Internet. ASes generally represent ISP networks,
large university networks, or government entities. Interdomain routing between these ASes is governed by BGP, and
individual ASes may have local preferences for how they wish to send packets along, but they cannot govern the paths
selected by other ASes. AS topology researchers often use measurement tools to create a picture of the global Internet.
These measurement tools, for instance BGP Updates from BGPStream \cite{BGPStream} or empirical paths from traceroute \cite{traceroute}, suffer from
incompleteness and innacuracies \cite{tracerouteProblems}.
\par
AS-level studies are further complicated by the lack of ground truth data for AS relationships and BGP paths. For AS relationships,
inference is often used based on economic considerations to classify the relationships of ASes. This was first done by Gao \cite{gao} by
maximizing the occurances of certain economic rules on the AS graph by choosing a particular set or relationships. This technique was only
evaluated against a single ISPs set of true relationships, however. As part of the CAIDA project, this inference technique was extended, leading
to the CAIDA AS-relationship dataset \cite{CAIDApaper}, \cite{CAIDA}. We choose these relationships for our purposes, and they are the current
research standard.
\par
Finding BGP paths is more of a challenge. Packet based simulations, wherein BGP is simulated directly, are computationally infeasible for the
scales relevant to a global study. An accurate, but realistic, simulation technique must be chosen to provide useful research potential in this regard.
The BGPSim algorithm \cite{quicksand} is one such simulation technique that is suitable for this study's purposes. BGPSim takes a set of AS relationships
as input, such as those provided by the CAIDA dataset \cite{CAIDA}, and returns routing trees based off of these relationships. These paths are found via
a modified breadth-first seach (BFS) algorithm. The BFS adds edges to routing trees first according to local preference (LP), then shortest path (SP), and finally tiebreak (TB).
A resulting routing tree contains all the equally reasonable paths (according to economic concerns) that exist between source ASes (within the routing tree) to 
destination ASes (the root of the routing tree). We find this technique suitable for our purposes, so we extend BGPSim 
(in ways explained further in this paper) as part of \toolname.

\section{Chokepoint Potential}

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{chokepoint}
	\captionof{figure}{Chokepoint potential example. ASes A,B, and C are all border nodes. 
						AS D is an internal node. ASes E and F are both external nodes.
						The out-to-in chokepoint potentials of A,B, and C are 0.25, 0.25, and 0.5 respectively.}\label{fig:chokepoint}
\end{Figure}

% Why Border ASes?
In order to identify AS chokepoints and compare nations, we need a measure that can be calculated from the many paths between
ASes. First, we decided to use a measure that is evaluated only on border ASes, or ASes that lie one hop from an AS belonging to another nation. 
We argue that this is intuitive because border
ASes are the first opportunity for nations to censor incoming traffic and the last opportunity for nations to block access to
foreign websites from within their borders. Additionally, while internal chokepoints may intercept many paths, those paths are required
to have entered through a border AS (in the case of out-to-in paths) or exit through a border AS (for in-to-out paths). This simplification has
the added benefit of making calculations more efficient.

% What is our measure, why does it make sense?
\par
We define the chokepoint potential of a border node to be the ratio of paths intercepted by that border node
to the number of paths intercepted by all other border nodes. Consider a border node $b$, belonging to country $c$.
If $P_c$ is the set of paths in to or out of country $c$ and $B_p$ is the set of border nodes within path $p$, then the
chokepoint potential of $b$, $CP_b$ is defined formally in equation \ref{eqn:chokePointPotential}. This measure captures
the relative strength exhibited by a border nodes in regards to what portion of paths it intercepts. This is calculated
seperately for in-to-out paths (those starting from a source in the country in question) and out-to-in paths.

% Formal Definition
\begin{equation}\label{eqn:chokePointPotential}
CP_b = \frac{|\{p \in P_c \textrm{ s.t. } \{b\} \subseteq B_p\}|}{\sum_{p \in P_c}|B_p|}
\end{equation}

\par
Given a set of BGP paths, this measure is an intuitive way to compare individual ASes and different nations. With this measure,
the chokepoint potential sum over all border nodes for a country is 1.0, as in, all of the border nodes collectively control the
flow of information over the nation's border. To compare one nation to another, we can inspect how many border nodes minimum are required
to obtain a certain chokepoint potential. The more border nodes required, the more difficult it would be for that nation to perform
censorship or surveillance. This is a clear way to differentiate nations based on the topology of their ASes.

\section{\toolname}

% Preprocessing and Data pipeline
\toolname is a new tool that calculates the chokepoint potential for every border AS given a set of AS relationships.
\toolname first takes the entire AS graph, as in from the CAIDA dataset \cite{CAIDA}, and uses the principles of BGPSim \cite{quicksand}
to generate a set of routing trees. These routing trees, as well as a set of AS country codes (for identifying which nation an AS belongs to)
are used to determine the chokepoint potentials for every border node. In our experiments, we used the country codes returned from Team Cymru's
IP to ASN whois service \cite{cymru}.

% Routing Tree Algorithm
\par
In order to calculate the routing trees, we use an extended version of the BGPSim algorithm developed by Gil et. al in \cite{quicksand}. In
our work we addressed the following limitations of BGPSim: (1) BGPSim returns a set of ASes for each path it considers but not the order in which
they are visited; (2) Once routing trees are determined, they cannot be accessed later without recalculation; (3) BGPSim relies on the outdated parallelization
framework DryadLinq for C\#. To address these issues, we use a Python implementation we dub BGPSimPy. BGPSimPy returns ordered paths from its routing trees,
saves routing trees to disk after calculation, and is parallelized with MPI via the mpi4py library. These improvements have the added benefit of yielding a cross platform
routing tree algorithm that is ready to work on most hardware.

% Chokepoint calculation
\par
Once BGPSimPy generates the routing trees, they can be processed to determine chokepoint potentials. This is done by iterating over every path between each AS-pair. Because
we use the same random tie-break as BGPSim, there is only 1 path between each AS-pair considered, even if multiple exist in the routing tree. Once a path is determined, it is
traversed. For each node visited, the number of paths intercepted by that node is incremented. This is done for both in-to-out paths and out-to-in paths, so only one traversal is
necessary per path. Additionally, the number of paths of each type that belong to each nation is tallied, as this makes up the denominator in equation \ref{eqn:chokePointPotential}.

\section{Experimental Setup}

% Chokepoint Evolution
There is ongoing research interest into ASes that intercept large portions of Internet paths \cite{throats}, \cite{decoy}. Some questions remain unanswered however. For instance, to what
extent does the current state of the Internet support national governments' attempts to censor Internet traffic? How does this vary from nation to nation? Is the Internet developing more
powerful chokepoints, or becoming more evenly accessible?
\par
To probe these questions we first used our chokepoint evaluation technique to investigate the chokepoint potential of all nations for the current Internet as well as the
change in chokepoint potentials over time. We looked at multiple snapshots of AS relationships from the CAIDA dataset (2012-2018).
For each timestamp, we generated routing trees based on these relationships. Then we calculated the chokepoint potential for every border node per snapshot. As a result we can investigate
how countries have changed overtime in their capability to enact censorship and surveillance. This is an attempt to understand what topological trends have developed historically.
With this test we can compare nations, and see which ones have overtime increased their capability to control the flow of information across their borders.

% Chokepoints and Internet Freedom
If chokepoint potential can be leveraged to determine if a nation can easily implement censorship, it stands to reason that their might already be a negative relationship between
the chokepoint potential of a nation and its Internet freedom. If a significant relationship were to be found it would strengthen chokepoint potential as a measure of a nation's censorship capability
and it would increase the value in monitoring chokepoint potentials across the globe.
\par
We tested whether a significant relationship exists between our measure of national chokepoints and a qualitative evaluation of Internet Freedom. For Internet Freedom we used
the Freedom House's Freedom On The Net report \cite{FOTN}. FOTN scores quantify the level of Internet freedom in countries. Each country receives a numerical score from 0 (the most free)
to 100 (the least free).
 To evaluate our measure, we first must define a way to rank each nation in regards to our chokepoint potential measure.
Acharya et al. \cite{throats} chose to determine how many ASes were needed (globally) to intercept 90\% of paths as a measure of the AS hierarchy. We choose a similar measure. Because we are
looking at national comparisons, however, we record how many border ASes are required to incercept 90\% of in-to-out or out-to-in paths for each nation. We compared this number
with each nation's (of those recorded by Freedom House) freedom on the net score.

\section{Results}
\subsection{Nations Over Time}

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{single_CN}
	\captionof{figure}{The evolution of China's in-to-out Chokepoint Potential}\label{fig:ChinaChokePoint}
\end{Figure}

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{single_US}
	\captionof{figure}{The evolution of the US's Chokepoint Potential}\label{fig:USChokePoint}
\end{Figure}

To inspect the changes over time for each nation we arrange all the border nodes belonging to a nation into a list. The list of border ASes is reverse sorted
so that the first AS has the highest chokepoint potential. The sum of all these nodes' chokepoint potential is 1.0. Then we step through the list, and record
the cumulative chokepoint potential of all the ASes seen so far. If we plot the number of ASes controled vs the cumulative chokepoint potential for that number
of ASes, we can see how many ASes are required for a certain nation to control different percentages of paths. We repeat this process for each snapshot to highlight
changes over time.

\par
For instance, consider figures \ref{fig:ChinaChokePoint} and \ref{fig:USChokePoint}. 
The x-axis (log-scale, so that countries with large differences in AS counts can be compared more easily)
is the number of border nodes controlled, and the y-axis is the ratio of in-to-out paths intercepted. Each line represents a different snapshot, with the more red lines being
farther in the past and more blue lines being more recent.

\par
The United States and China are shown here to exhibit their dramatic differences. First, it is worth pointing out that the United States has many more ASes than China, hence
it's line extends further to the right in these plots. We also see that China, in all cases, can control a much larger portion of its paths with much fewer ASes than the
United States. This result is entirely expected. Of more interest is the trends that can be seen over time. China clearly has developed an AS topology such that very few
ASes can intercept nearly all BGP paths. The US has evolved in a different way. While it has become somewhat easier for the US to intercept most of its paths, it has become
more difficult to intercept around 70\% of its paths and higher. This suggest an expansion of ASes on the interior and more connections, as well as a strengthening of
the very top ASes.

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{single_DE}
	\captionof{figure}{The evolution of Germany's in-to-out Chokepoint Potential}\label{fig:GermChokePoint}
\end{Figure}

\par
Not all nations have evolved to a state where it easier to control paths. One example is Germany, as shown in figure \ref{fig:GermChokePoint}. For Germany, a fairly constant
trend shows that it has become more difficult to intercept BGP paths. Unlike the other examples, any amount of German border ASes intercept less paths in more recent tests.

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{NodesNeeded}
	\captionof{figure}{Number of ASes to intercept 90\% of ito paths for multiple nations over time}\label{fig:nodes}
\end{Figure}

\par
In order to compare multiple nations, we have plotted the number of ASes needed to intercept 90\% of in-to-out paths
for each timestamp recorded. These results are detailed in figure \ref{fig:nodes}.

\subsection{Internet Freedom}

In our test of the relationship between Internet Freedom and chokepoint potential, we plotted the Freedom on the Net score
of each nation vs the number of border ASes that that nation needed to in order to intercept 90\% of in-to-out paths. Additionally,
we evaluated the relationship with an Ordinarly Least Squares (OLS) fit, and found that the relationship was statistically significant,
with a p-value $\leq$ 0.002 for 2017. The relationship held for other timestamps as well. The results for 2017 are shown in figure \ref{fig:fotn2017}

\begin{Figure}
	\centering
	\includegraphics[width=\linewidth]{fotn2017}
	\captionof{figure}{Number of ASes to intercept 90\% of ito paths vs Freedom On The Net Score (2017)}\label{fig:fotn2017}
\end{Figure}

\par
For each timestamp we see what appears to be two general modes of behavior. Nations that are not free or partly free tend to requrie few ASes
to intercept 90\% of their paths. Free nations on the otherhand require varying degrees of large numbers of ASes to control the same portion
of their paths. There are interesting outliers for both situations, however. Countries like Estonia (EE) or Iceland (IS) are very free but require
few nodes to control most of their paths. The reason for these outliers is likely that their overall AS counts are very low. On the other hand, Russia (RU)
is a very interesting outlier in that it is found to be not free by FOTN, but requires a large number of ASes to control most of its paths. This suggests
that the censorship efforts in Russia might be of types that do not require AS level chokepoints.

@@

@@

We are not the first to investigate the relationship between Internet freedom and
AS-level topology. Similar techniques have been used to classify nations according
to the connectivity of their ASes \cite{politicsrouting}. This has only been done for a
single moment in time, however, making the results limited in terms of stability and predictability.
Additionaly, previous work has not used country level chokepoints as the link between Internet topology
and censorship or surveillance practices. The work in \cite{politicsrouting} chose to relate Internet topology
to the Freedom of the Press measure from freedom house instead of the Freedom On The Net score. They chose to do this
to include more nations. Additionally, this study didn't include the United States and Russia in their experiments because they were
outliers in regards to their topologies. Through our approach we hope to extend this previous work by finding an interesting measure for
understanding the dynamics of all nations, as well as targeting our results more specifically to Internet freedom by using the Freedom On
The Net score as our measure for Internet freedom. Through our techniques, we provide a simple measure that not only 
sheds light on the relationship between topology and Internet freedom, but reveals currently free
nations that could easily implement censorship if their governments decided to.

@@

\subsection{Routing Trees Dataset}
In the hope to further AS topology research, we have open sourced the routing tree datasets generated in this study. While we generated routing trees
with an efficient algorithm, it still requires considerable time to calculate them, particulary for multiple timestamps. Additionally, each set of routing trees
takes up on the order of 50GB of disk space. By releasing these datasets we hope that researchers looking for a particular set of routing trees will find
working with these simpler than recalculating them. This also provides an alternative to research projects that might otherwise use measurement tools to estimate
BGP paths.

% Points of Presence

\subsection{Future Work}
% OONI data
While linking chokepoint potential to FOTN scores is a substantial contribution, it still stands that FOTN can serve only as a proxy for censorship.
This is useful for large trends and general understanding, but a more fine-grained approach could be used to interpret the direct connection between
actual censorship events and the shifts in the AS graph. The Open Observatory of Network Interference, or OONI, \cite{OONI} provides Internet users around
the world with a tool called the ooniprobe. The ooniprobe lets users run a suite of tests to identify censorship anamolies of various types, and the results are
recorded in the large OONI database. Matching up changes in OONI measurements, such as increased censorship campaigning in an authoritarian nation, with shifts
in chokepoint potential would be a major step in understanding the interplay of censorship and AS-level chokepoints. This process involves designing a way to classify
censorship events and chokepoint potential changes, and as such lies beyond the scope of this study.
